Are environmental and geographic variables effective surrogates for genetic variation in conservation planning?

### 2016-05-07 code/rmarkdown/article.Rmd
+ article fixes
Former-commit-id: c2182da5b3d06da50c4bf34c2905e8b170c11b6f

<!-- surrogacy analysis -->
The environmental and geographic variables were moderately effective surrogates for genetic variation in most species (Figure 2). The relationship between the proportion of adaptive genetic variation secured in a prioritization and the proportion environment variation it also secured differed depending on the species for which the prioritization was generated ($\chi^2_{r env.surrogacy.AOV$df[[4]]} = {`r round(env.surrogacy.AOV$Resid..Dev[[4]],2)`} P = pvalString(`r env.surrogacy.AOV$Pr..Chi.[[4]]`)$). The slope for each species were all significantly different to zero (minimum \textit{z} = `r round(min(env.surrogate.spp.DF$statistic),2)`; maximum $P = `r  pvalString(max(env.surrogate.spp.DF$p.value))`$; Table S3). The explanatory power of the environmental surrogates were also generally quite high for most species (mean `r round(mean(env.surrogate.spp.DF$r2CU),2)` $R^2 \pm$ `r round(sd(env.surrogate.spp.DF$r2CU),2)` SD; Figure S56), with exception to _Carex sempervirens_. The nature of these relationships suggest that most of the adaptive variation for a given species can be secured in a prioritization using moderately high environmental-based targets. Similarly, the proportion of neutral genetic variation in a prioritization was affected by the interaction between species and the proportion of neutral variation secured in the prioritization ($\chi^2_{r geo.surrogacy.AOV$df[[4]]} = `r round(geo.surrogacy.AOV$Resid..Dev[[4]],2)`$; $P$ = `r pvalString(geo.surrogacy.AOV$Pr..Chi.[[4]])`). The slope for each species were also significantly different to zero (minimum $z value = `r min(geo.surrogate.spp.DF$statistic)`$; maximum $P = `r max(env.surrogate.spp.DF$p.value)`; Table S3). Generally, the explanatory power of geographic variables were higher than that of environmental variables (mean `r round(mean(geo.surrogate.spp.DF$r2CU),2)` $R^2 \pm$ `r round(sd(geo.surrogate.spp.DF$r2CU),2)` SD; Figure S57). Compared to the environmental variables, the slopes of the relationships suggest that very high geographic-based targets are required to generate prioritizations that secure a sufficient proportion of neutral genetic variation for most species. Additionally, all species were associated with prioritizations that secured a large proportion of environmental or geographic variation (> 70 %), yet preserved only a very small proportion of the genetic variation (< 10 %). These results suggest while prioritizations generated using surrogate-based targets tend to secure more genetic variation, prioritizations generated using just these targets can result in poor solutions.

>>>>

<!-- surrogacy analysis -->
The environmental and geographic variables were moderately effective surrogates for genetic variation in most species (Figure 2). The relationship between the proportion of adaptive genetic variation secured in a prioritization and the proportion environment variation it also secured differed depending on the species for which the prioritization was generated ($\chi^2_{`r env.surrogacy.AOV$df[[4]]`} = {`r round(env.surrogacy.AOV$Resid..Dev[[4]],2)`} P = pvalString(`r env.surrogacy.AOV$Pr..Chi.[[4]]`)$). The slope for each species were all significantly different to zero (minimum \textit{z} = `r round(min(env.surrogate.spp.DF$statistic),2)`; maximum $P = `r  pvalString(max(env.surrogate.spp.DF$p.value))`$; Table S3). The explanatory power of the environmental surrogates were also generally quite high for most species (mean `r round(mean(env.surrogate.spp.DF$r2CU),2)` $R^2 \pm$ `r round(sd(env.surrogate.spp.DF$r2CU),2)` SD; Figure S56), with exception to _Carex sempervirens_. The nature of these relationships suggest that most of the adaptive variation for a given species can be secured in a prioritization using moderately high environmental-based targets. Similarly, the proportion of neutral genetic variation in a prioritization was affected by the interaction between species and the proportion of neutral variation secured in the prioritization ($\chi^2_{`r geo.surrogacy.AOV$df[[4]]`} = `r round(geo.surrogacy.AOV$Resid..Dev[[4]],2)`$; $P$ = `r pvalString(geo.surrogacy.AOV$Pr..Chi.[[4]])`). The slope for each species were also significantly different to zero (minimum $z value = `r min(geo.surrogate.spp.DF$statistic)`$; maximum $P = `r max(env.surrogate.spp.DF$p.value)`; Table S3). Generally, the explanatory power of geographic variables were higher than that of environmental variables (mean `r round(mean(geo.surrogate.spp.DF$r2CU),2)` $R^2 \pm$ `r round(sd(geo.surrogate.spp.DF$r2CU),2)` SD; Figure S57). Compared to the environmental variables, the slopes of the relationships suggest that very high geographic-based targets are required to generate prioritizations that secure a sufficient proportion of neutral genetic variation for most species. Additionally, all species were associated with prioritizations that secured a large proportion of environmental or geographic variation (> 70 %), yet preserved only a very small proportion of the genetic variation (< 10 %). These results suggest while prioritizations generated using surrogate-based targets tend to secure more genetic variation, prioritizations generated using just these targets can result in poor solutions.
